---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

```{R}
rawDAct <- read.csv("activity.csv")

DAct <- na.omit(rawDAct) ### remove na data
```

## What is mean total number of steps taken per day?
```{r}
StepsDayMean <-aggregate(DAct$steps, 
                list(day = DAct$date),
                mean)
```


####Output Mean
```{r}

print(StepsDayMean)
```



## What is median total number of steps taken per day?
```{r}
StepsDayMedian <-aggregate(DAct$steps, 
                list(day = DAct$date),
                FUN = median)
```


####Output Median
```{r}
print(StepsDayMedian)

```




### Plot histogram of steps-day

```{r}
StepsDaySum <-aggregate(DAct$steps, 
                list(day = DAct$date),
                sum)

hist(StepsDaySum$x, main = "Historgram of Steps per day")


```


## What is the average daily activity pattern?
```{r}

plot(StepsDayMean$day,StepsDayMean$x, type = "l",  main = "Average Daily Activity Pattern")

```


####Max Steps

```{r}
MaxStepsIn5Min <- max(DAct$steps)

MaxStepInterval<- DAct$interval[DAct$steps==MaxStepsIn5Min]
DayOfMaxStepInterval <- round(615/12/24)

print(MaxStepsIn5Min)


```



## Imputing missing values

###The number of incomplete cases is
```{r}
print(nrow(rawDAct)-nrow(DAct))

```

####Strategy 1 replacing NA with mean
```{r}

for(i in 1:nrow(rawDAct)){
  newDAct[is.na(rawDAct[i,]), i] <- mean(rawDAct[i,], na.rm = TRUE)
}
```
###newDACT Daily Average Histogram
```{r}


newStepsDaySum <-aggregate(newDAct$steps, 
                list(day = newDAct$date),
                sum)

hist(newStepsDaySum$x, main = "Historgram of Steps of per day(imputed data)")


```
###Calucluate and report the mean and media for 





####Mean
```{r}
print(mean(newStepsDaySum$x))

```

####Media

```{r}
print(median(newStepsDaySum$x))
```








## Are there differences in activity patterns between weekdays and weekends?
